---
title: "assignment4"
author: "Louis Duverger"
date: "6/11/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warnings = FALSE)
```

## Introduction

For this study, we will use the mtcars data set and ones of its favariables.

The purpose of this presentation is to study the impact of the cylinders on the evolution of the miles per galon by horse power. 

First we will see how the cylinders are mapped to the clusters of mpg/hp. Then we will see if this clusters tend to show any linear pattern.

## Clusters

Lets see on one hand, how miles per gallon and horsepower are related, and how miles per galon are related to cylinders on the other hand.

```{r, eval= TRUE, echo=FALSE}
library(plotly)
library(dplyr)
a <- plot_ly(data = mtcars, x = ~hp, y = ~mpg, type = "scatter", mode = "markers")
b <- plot_ly(data = mtcars, y = ~mpg, color = ~(as.factor(cyl)), type = "box") %>% layout(title = "Mpg by hp (left), Mpg by cyl(right)")
subplot(a,b)
```


## Cluster and tendance

```{r, eval = TRUE, echo=FALSE}
model <-  lm(data = mtcars, mpg ~hp*I(as.factor(cyl))-1)
model$coefficients[1:4]
```

We can see that the different number of cylinders have an impact. Furthermore they seem to be significant looking at their p-value.

```{r}
summary(model)$coef[1:4,]
```


## All combined
```{r}
library(ggplot2)
g <- ggplot(data=mtcars, aes(x=hp,y=mpg, color = as.factor(cyl)))+geom_point()+geom_smooth(method = "lm", se=FALSE)
ggplotly(g)
```

Now, feel free to use the Shiny app I made to play more fluidly with this plot.
